Investigation on GIT

### 2010-04-25 paper.tex
agregue algo de performance

Operations being done offline also means that there is no network latency to be worried of,
and can be more performant. Performance is important in VCS because if the revision
system is too slow, it might affect the workflow of the tool. Operations like commits, 
searching through the history, taking the diff out of two branches,  
% Explicaremos el principio de funcionamiento de la herramienta distribuida 
% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
% su propio repositorio, que las versiones pueden ser infinitas (por más que 
% haya una(s) maestra(s)), que se puede trabajar offline, etc.

>>>>

\subsection{Performance}

Operations being done offline also means that there is no network latency to be worried of,
and can be more performant. Performance is important in VCS because if the revision
system is too slow, it might affect the workflow of the tool. Operations like commits, 
searching through the history, taking the diff out of two branches, and especially merging
if not done fast enough are limiting what you can do with it, the impact of this depending of 
the size of the repository.
% Explicaremos el principio de funcionamiento de la herramienta distribuida 
% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
% su propio repositorio, que las versiones pueden ser infinitas (por más que 
% haya una(s) maestra(s)), que se puede trabajar offline, etc.
